---
title: "Weight of Fish"
author: "Daniela Olvera-Mota"
date: "Fall 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight
We will find the best model by using two variables to predict the weight of the perch,then we will compare this to the model that is best overall.

## Perch

```{r}
perch=filter(fish, Species == "Perch")
```

### Best Two regressor model

```{r}
modelPerch= regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data=perch)
summary(modelPerch)
```

```{r}
best2Perch = lm(Weight ~ Height + Width, data = perch)
summary(best2Perch)
```

## best 2-variable equation
Weight = -536 + 74.77*Height+ 69.62*Width

## Pike

```{r}
pike=filter(fish, Species == "Pike")
```

### Best Two regressor model

```{r}
modelPike= regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data=pike)
summary(modelPike)
```

```{r}
best2Pike = lm(Weight ~ Length1 + Length3, data = pike)
summary(best2Pike)
```

## best 2-variable equation
Weight = -1675.79 + -105.64*Length1+ 141.25*Length3

## Roach

```{r}
roach=filter(fish, Species == "Roach")
```

### Best Two regressor model

```{r}
modelRoach= regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data=roach)
summary(modelRoach)
```

```{r}
best2Roach = lm(Weight ~ Length3 + Width, data = roach)
summary(best2Roach)
```

## best 2-variable equation
Weight = -319.118 + 8.278*Length3+ 72.300*Width

## Final Summary Statements

For the perch variable,  the best two regression model would be Height and Width. For the pike variable, the best two regression model would be Length1 and Length3. For the roach variable, the best two regression model would be Length3 and Width. 